Advanced Reactor Fuel Cycles Molten Salt Reactor Design

### 2017-01-05 MSR-design.tex
Update MSRE/MSBR material compositions.

>>>>

\subsection{\gls{ARFC} \gls{MSRE} Model Design Execution}

\subsubsection{Interpolation table generation}

The fuel salt density dependence on temperature is based on the \gls{FLiBe}
density correlation in \cite{serrano-lopez_molten_2013}:

\begin{equation}
  \label{eq:flibe_density}
  \rho(kg/m^3) = 2413.03-0.4884\cdot T(K)
\end{equation}

This does not account for the change in density introduced by dissolution of
fuel components in the salt. At the average fuel salt temperature in the
reactor, the \gls{FLiBe} correlation predicts a density of 1.96
grams/cm$^3$. This differs from the measured values in the \gls{MSRE} of 2.24,
2.08, and 2.14 grams/cm$^3$ for thorium-uranium, highly-enriched uranium, and
partially-enriched uranium fuel salts respectively. Moderator density is
currently considered to be constant and equal to 1.843 grams/cm$^3$
\cite{cammi_multi-physics_2011}.

Group constants required for eigenvalue calculation:

\begin{equation}
  \label{eq:constants}
  D_g,\Sigma_{rg},\Sigma_{sg'g},\chi_g,\nu_g\Sigma_{fg},\kappa
\end{equation}

Additionally, $v_g$ is required for transient calculations.
